---
title: "Introduction to generics"
author: "Charles Determan Jr."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to generics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is the \CRANpkg{generics} package developed primarily as a support package
in the subsequent development of additional packages for the CRAN ecosystem.  Many 
R packages that leverage the S4 OOP system must define their own generics via 
\Rcode{setGeneric}.  As many functions are applicable across packages this package provides
a centralized collection of generics to avoid the need to create package specific generic
functions.  This additionally ensures that generics are explicitly defined whereby they will
be searched and avoid the possible masking by other packages.

## Basic Example

Here is a basic example that demonstrates the typical way to create a new
method for an S4 generic function.  The only difference is that the \Rfunction{setGeneric}
does not need to be called.

```{r, eval=FALSE}
library(generics)
setClass("myClass")
setClass("A", contains="myClass")
setMethod("typeof", signature(x="myClass"),
          function(x) {
            print('typeof was called')
            switch(class(x),
                   "A" = "myClassA",
                   "B" = "myClassB",
                   stop("unrecognized class"))
          })

```

## Developing Packages

The above example is only applicable in a single R session.  But what about
when you create a new R package?  In that case you simply need to import the 
relevant generic function.  The following would be how you would use roxygen2
to import the \Rfunction{typeof} generic for setting methods.

```{r, eval = FALSE}
#' @importFrom generics typeof
#' @import methods
#' @export
setMethod('typeof', signature(x="myClass"),
          function(x) {
            print('typeof was called')
            switch(class(x),
                   "A" = "myClassA",
                   "B" = "myClassB",
                   stop("unrecognized class"))
          })

```
